checkData

### 2023-08-29 analysis/checkData.Rmd
Code to COPE status
currently alters primary coded values only

>>>>

#Add COPE status FROM PRACTICE CODING, does not alter main d_journals tibble
```{r}
# Load googlesheet data

dj_prominent <- read_csv(here('data','raw', 'journalList_PROMINENT.csv')) %>% #loads csv of googlesheet data of prominent journals
  slice_head(n = 114) %>%
  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )

dj_random <- read_csv(here('data','raw', 'journalList_RANDOM.csv')) %>% #loads csv of googlesheet data of random journals
  slice_head(n = 108) %>%
  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )

# Combine above CSVs to one tibble

dj_cope <- bind_rows(dj_prominent, dj_random)

# Identify duplicate rows
duplicates <- duplicated(dj_cope)

# Select the duplicate rows
duplicate_rows <- dj_cope[duplicates, ]

# Check if duplicate rows have the same COPE values for journals
for (i in seq_len(nrow(duplicate_rows))) {
  row <- duplicate_rows[i, ]
  id <- row$ID
  value <- row$Value
  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)

  if (same_values) {
    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
  } else {
    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
  }
}

#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
dj_cope <- distinct(dj_cope, journal, .keep_all = T)

#join with main data tibble:
d_primaryONLY <- left_join(d_primaryONLY, dj_cope, by = 'journal')
